---
title: "UFML Thesis"
author: "Femke van Boheemen"
date: "2025-05-15"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: yeti
    self_contained: false
    vertical_layout: fill
---

<style>
.sbframe_commentary {
  width: 400px;
}
</style>

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(plotly)
data_clean <- read_excel("UFML - 14 mei.xlsx", sheet = 2, skip = 1)
data_filtered <- data_clean %>% 
  filter(!is.na(Q24))

```



### UFML 1 Comparison interactive


```{r interactive-violin-a}

a <- ggplot(data_filtered, aes(x = factor(Q24), y = Identiteit_socialeverbinding, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "UFML 1 Identity and Social Bonding", 
       x = "", 
       y = "Frequency of use (1 = Never, 5 = Very often)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 5), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(a)
```
***
uitleg hihi

### UFML 2 Comparison interactive

```{r interactive-violin-b}

b <- ggplot(data_filtered, aes(x = factor(Q24), y = Emotieregulatie, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "UFML 2 Emotion Regulation", 
       x = "", 
       y = "Frequency of use (1 = Never, 5 = Very often)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 5), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(b)
```

***

lol uitleg

### UFML 3 Comparison interactive


```{r interactive-violin-c}

c <- ggplot(data_filtered, aes(x = factor(Q24), y = Focus_concentratie, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "UFML 3 Focus and Concentration", 
       x = "", 
       y = "Frequency of use (1 = Never, 5 = Very often)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 5), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(c)
```
***
uitleg yuhyuh

### UFML 4 Comparison interactive


```{r interactive-violin-d}

d <- ggplot(data_filtered, aes(x = factor(Q24), y = Achtergrond_gezelschap, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "UFML 4 Background and Company", 
       x = "", 
       y = "Frequency of use (1 = Never, 5 = Very often)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 5), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(d)
```
***
uitleg hihi

### UFML 5 Comparison interactive


```{r interactive-violin-e}

e <- ggplot(data_filtered, aes(x = factor(Q24), y = Fysiologischeopwinding, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "UFML 5 Fysiological Arousal", 
       x = "", 
       y = "Frequency of use (1 = Never, 5 = Very often)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 5), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(e)
```
***
uitleg hihi

### SPWB 1 Comparison interactive


```{r interactive-violin-f}

f <- ggplot(data_filtered, aes(x = factor(Q24), y = Autonomie, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "SPWB 1 Autonomy", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(f)
```
***
uitleg hihi

### SPWB 2 Comparison interactive


```{r interactive-violin-g}

g <- ggplot(data_filtered, aes(x = factor(Q24), y = Omgevingsbeheersing, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "SPWB 2 Environmental management", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(g)
```
***
uitleg hihi

### SPWB 4 Comparison interactive


```{r interactive-violin-h}

h <- ggplot(data_filtered, aes(x = factor(Q24), y = `Positieve relaties`, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "SPWB 4 Positive relations", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(h)
```
***
uitleg hihi

### SPWB 4 Comparison interactive


```{r interactive-violin-i}

i <- ggplot(data_filtered, aes(x = factor(Q24), y = `Persoonlijke groei`, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "SPWB 3 Personal Growth", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(i)
```
***
uitleg hihi

### SPWB 5 Comparison interactive


```{r interactive-violin-j}

j <- ggplot(data_filtered, aes(x = factor(Q24), y = `Doel in het leven`, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "SPWB 5 Goal in Life", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(j)
```
***
uitleg hihi

### SPWB 6 Comparison interactive


```{r interactive-violin-k}

k <- ggplot(data_filtered, aes(x = factor(Q24), y = `Zelfacceptatie`, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() + 
  labs(title = "SPWB 6 Self Acceptance", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(k)
```
***
uitleg hihi

### UFML 1 vs SPWB 1 Comparison interactive


```{r interactive-correlation-l}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

l <- ggplot(data_filtered, aes(x = Autonomie, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Autonomy and Identity/Social connection per group",
    x = "Autonomy\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(l)

```
***
uitleg hihi

### UFML 1 vs SPWB 2 Comparison interactive


```{r interactive-correlation-m}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

m <- ggplot(data_filtered, aes(x = Omgevingsbeheersing, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Environmental Management and Identity/Social connection per group",
    x = "Environmental Management\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(m)

```
***
uitleg hihi

### UFML 1 vs SPWB 3 Comparison interactive


```{r interactive-correlation-n}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

n <- ggplot(data_filtered, aes(x = `Persoonlijke groei`, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Personal Growth and Identity/Social connection per group",
    x = "Personal Growth\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(n)

```
***
uitleg hihi

### UFML 1 vs SPWB 4 Comparison interactive


```{r interactive-correlation-o}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

o <- ggplot(data_filtered, aes(x = `Positieve relaties`, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Positive Relations and Identity/Social connection per group",
    x = "Positive Relations\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(o)

```
***
uitleg hihi

### UFML 1 vs SPWB 5 Comparison interactive


```{r interactive-correlation-p}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

p <- ggplot(data_filtered, aes(x = `Doel in het leven`, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Goal in Life and Identity/Social connection per group",
    x = "Goal in Life\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(p)

```
***
uitleg hihi

### UFML 1 vs SPWB 6 Comparison interactive


```{r interactive-correlation-q}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

q <- ggplot(data_filtered, aes(x = Zelfacceptatie, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Self Acceptance and Identity/Social connection per group",
    x = "Self Acceptance\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(q)

```
***
uitleg hihi


### UFML 2 vs SPWB 1 Comparison interactive


```{r interactive-correlation-r}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

r <- ggplot(data_filtered, aes(x = Autonomie, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Autonomy and Emotion Regulation per group",
    x = "Autonomy\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(r)

```
***
uitleg hihi

### UFML 2 vs SPWB 2 Comparison interactive


```{r interactive-correlation-s}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

s <- ggplot(data_filtered, aes(x = Omgevingsbeheersing, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Environmental Management and Emotion Regulation per group",
    x = "Environmental Management\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(s)

```
***
uitleg hihi

### UFML 2 vs SPWB 3 Comparison interactive


```{r interactive-correlation-t}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

t <- ggplot(data_filtered, aes(x = `Persoonlijke groei`, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Personal Growth and Emotion Regulation per group",
    x = "Personal Growth\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(t)

```
***
uitleg hihi

### UFML 2 vs SPWB 4 Comparison interactive


```{r interactive-correlation-u}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

u <- ggplot(data_filtered, aes(x = `Positieve relaties`, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Positive Relations and Emotion Regulation per group",
    x = "Positive Relations\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(u)

```
***
uitleg hihi

### UFML 2 vs SPWB 5 Comparison interactive


```{r interactive-correlation-v}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

v <- ggplot(data_filtered, aes(x = `Doel in het leven`, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Goal in Life and Emotion Regulation per group",
    x = "Goal in Life\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(v)

```
***
uitleg hihi

### UFML 2 vs SPWB 6 Comparison interactive


```{r interactive-correlation-w}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

w <- ggplot(data_filtered, aes(x = Zelfacceptatie, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Self Acceptance and Emotion Regulation per group",
    x = "Self Acceptance\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(w)

```
***
uitleg hihi

### UFML 3 vs SPWB 1 Comparison interactive


```{r interactive-correlation-x}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

x <- ggplot(data_filtered, aes(x = Autonomie, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Autonomy and Focus/Concentration per group",
    x = "Autonomy\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus/Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(x)

```
***
uitleg hihi

### UFML 3 vs SPWB 2 Comparison interactive


```{r interactive-correlation-y}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

y <- ggplot(data_filtered, aes(x = Omgevingsbeheersing, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Environmental Management and Focus/Concentration per group",
    x = "Environmental Management\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus and Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(y)

```
***
uitleg hihi

### UFML 3 vs SPWB 3 Comparison interactive


```{r interactive-correlation-z}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

z <- ggplot(data_filtered, aes(x = `Persoonlijke groei`, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Personal Growth and Focus/Concentration per group",
    x = "Personal Growth\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus and Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(z)

```
***
uitleg hihi

### UFML 3 vs SPWB 4 Comparison interactive


```{r interactive-correlation-aa}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

aa <- ggplot(data_filtered, aes(x = `Positieve relaties`, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Positive Relations and Focus/Concentration per group",
    x = "Positive Relations\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus and Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(aa)

```
***
uitleg hihi

### UFML 3 vs SPWB 5 Comparison interactive


```{r interactive-correlation-ab}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ab <- ggplot(data_filtered, aes(x = `Doel in het leven`, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Goal in Life and Focus/Concentration per group",
    x = "Goal in Life\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus and Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ab)

```
***
uitleg hihi

### UFML 3 vs SPWB 6 Comparison interactive


```{r interactive-correlation-ac}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ac <- ggplot(data_filtered, aes(x = Zelfacceptatie, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Self Acceptance and Focus/Concentration per group",
    x = "Self Acceptance\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus and Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ac)

```
***
uitleg hihi

### UFML 4 vs SPWB 1 Comparison interactive


```{r interactive-correlation-ad}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ad <- ggplot(data_filtered, aes(x = Autonomie, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Autonomy and Background/Company per group",
    x = "Autonomy\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Achtergrond and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ad)

```
***
uitleg hihi

### UFML 4 vs SPWB 2 Comparison interactive


```{r interactive-correlation-ae}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ae <- ggplot(data_filtered, aes(x = Omgevingsbeheersing, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Environmental Management and Background/Company per group",
    x = "Environmental Management\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Bachground and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ae)

```
***
uitleg hihi

### UFML 4 vs SPWB 3 Comparison interactive


```{r interactive-correlation-af}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

af <- ggplot(data_filtered, aes(x = `Persoonlijke groei`, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Personal Growth and Background/Company per group",
    x = "Personal Growth\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Background and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(af)

```
***
uitleg hihi

### UFML 4 vs SPWB 4 Comparison interactive


```{r interactive-correlation-ag}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ag <- ggplot(data_filtered, aes(x = `Positieve relaties`, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Positive Relations and Background/Company per group",
    x = "Positive Relations\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Background and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ag)

```
***
uitleg hihi

### UFML 4 vs SPWB 5 Comparison interactive


```{r interactive-correlation-ah}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ah <- ggplot(data_filtered, aes(x = `Doel in het leven`, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Goal in Life and Background/Company per group",
    x = "Goal in Life\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Background and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ah)

```
***
uitleg hihi

### UFML 4 vs SPWB 6 Comparison interactive


```{r interactive-correlation-ai}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ai <- ggplot(data_filtered, aes(x = Zelfacceptatie, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Self Acceptance and Background/Company per group",
    x = "Self Acceptance\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Background and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ag)

```
***
uitleg hihi

### UFML 5 vs SPWB 1 Comparison interactive


```{r interactive-correlation-aj}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

aj <- ggplot(data_filtered, aes(x = Autonomie, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Autonomy and Fysiological Arousal per group",
    x = "Autonomy\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(aj)

```
***
uitleg hihi

### UFML 5 vs SPWB 2 Comparison interactive


```{r interactive-correlation-ak}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ak <- ggplot(data_filtered, aes(x = Omgevingsbeheersing, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Environmental Management and Fysiological Arousal per group",
    x = "Environmental Management\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ak)

```
***
uitleg hihi

### UFML 5 vs SPWB 3 Comparison interactive


```{r interactive-correlation-al}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

al <- ggplot(data_filtered, aes(x = `Persoonlijke groei`, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Personal Growth and Fysiological Arousal per group",
    x = "Personal Growth\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(al)

```
***
uitleg hihi

### UFML 5 vs SPWB 4 Comparison interactive


```{r interactive-correlation-am}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

am <- ggplot(data_filtered, aes(x = `Positieve relaties`, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Positive Relations and Fysiological Arousal per group",
    x = "Positive Relations\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(am)

```
***
uitleg hihi

### UFML 5 vs SPWB 5 Comparison interactive


```{r interactive-correlation-an}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

an <- ggplot(data_filtered, aes(x = `Doel in het leven`, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Goal in Life and Fysiological Arousal per group",
    x = "Goal in Life\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(an)

```
***
uitleg hihi

### UFML 5 vs SPWB 6 Comparison interactive


```{r interactive-correlation-ao}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ao <- ggplot(data_filtered, aes(x = Zelfacceptatie, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Self Acceptance and Fysiological Arousal per group",
    x = "Self Acceptance\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ao)

```
***
uitleg hihi