---
title: "UFML Thesis"
author: "Femke van Boheemen"
date: "2025-05-15"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: yeti
    self_contained: false
    vertical_layout: fill
---

<style>
.sbframe_commentary {
  width: 400px;
}
</style>

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(plotly)
library(ggpubr)
library(kableExtra)
library(knitr)
data_clean <- read_excel("UFML - 14 mei.xlsx", sheet = 2, skip = 1)
data_filtered <- data_clean %>% 
  filter(!is.na(Q24))

```



### UFML 1 Comparison interactive

```{r utest-a, echo=FALSE, results='hide'}

wilcox.test(Identiteit_socialeverbinding ~ Q24, data = data_filtered)
```

```{r interactive-violin-a}

a <- ggplot(data_filtered, aes(x = factor(Q24), y = Identiteit_socialeverbinding, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 5) + 
  labs(title = "UFML 1 Identity and Social Bonding", 
       x = "", 
       y = "Frequency of use (1 = Never, 5 = Very often)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 5), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(a)
```
***
**Expectation**  
Students use music more for its functions in Identity and Social Bonding than employed individuals. (students have more social events and are more prone to having to meet new groups/environments)

**Interpretation**  
- Students use music more frequently for identity and social bonding than employed individuals.  
- Students show a higher median and more responses at the upper end (3–4).  
- Employed individuals have a lower median and a wider spread toward lower values (1–2).  
- The P-value = 0.041, indicating a statistically significant difference.  

Students rely more on music for identity and social bonding, maybe because of musics role in self-exploration and social connection during young adulthood.

### UFML 2 Comparison interactive

```{r utest-b, echo=FALSE, results='hide'}

wilcox.test(Emotieregulatie ~ Q24, data = data_filtered)
```

```{r interactive-violin-b}

b <- ggplot(data_filtered, aes(x = factor(Q24), y = Emotieregulatie, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 5) + 
  labs(title = "UFML 2 Emotion Regulation", 
       x = "", 
       y = "Frequency of use (1 = Never, 5 = Very often)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 5), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(b)
```

***

**Expectation**  
Students and employed individuals both frequently use music for its functions in Emotion regulation, but students use it more intensively (still figuring out how to deal with (new) emotions)  

**Interpretation**  
- Both students and employed individuals use music frequently for emotion regulation (ratings mostly between 3–4).  
- Students show a slightly wider spread towards higher values (4–5), suggesting somewhat more intensive use.  
- Medians and means are similar across groups.  
- The p-value = 0.15, indicating no statistically significant difference.  

While students may use music slightly more for emotion regulation, this difference is not statistically significant. The data suggests similar usage patterns across both groups.  

### UFML 3 Comparison interactive

```{r utest-c, echo=FALSE, results='hide'}

wilcox.test(Focus_concentratie ~ Q24, data = data_filtered)
```

```{r interactive-violin-c}

c <- ggplot(data_filtered, aes(x = factor(Q24), y = Focus_concentratie, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 5) + 
  labs(title = "UFML 3 Focus and Concentration", 
       x = "", 
       y = "Frequency of use (1 = Never, 5 = Very often)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 5), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(c)
```
***
**Expectation**  
Students use music more frequently for its functions in focus and concentration. (more opportunity to study with music)  

**Interpretation**  
- Students use music more frequently for focus and concentration than employed individuals.  
- Students show a higher median and greater density at the top end (4–5).  
- Employed individuals have a slightly lower median and a broader spread across the scale.  
- The p-value = 0.023, indicating a statistically significant difference.  

Students use music more to support focus and concentration, possibly reflecting their academic demands and structured study environments.

### UFML 4 Comparison interactive

```{r utest-d, echo=FALSE, results='hide'}

wilcox.test(Achtergrond_gezelschap ~ Q24, data = data_filtered)
```

```{r interactive-violin-d}

d <- ggplot(data_filtered, aes(x = factor(Q24), y = Achtergrond_gezelschap, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 5) + 
  labs(title = "UFML 4 Background and Company", 
       x = "", 
       y = "Frequency of use (1 = Never, 5 = Very often)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 5), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(d)
```
***
**Expectation**  
Students use music more for background and accompaniment than employed individuals (studenten zijn eenzamer en hebben meer flexibiliteit in omgeving)  

**Interpretation**  
- Students appear to use music slightly more for background and company than employed individuals.  
- Students have a higher median and more responses clustered around 4.  
- Employed individuals show a broader spread and slightly lower median.  
- The p-value = 0.078, indicating the difference is not statistically significant, but nearing significance.  

There is a weak trend suggesting students may use music more for background and company, but the difference is not statistically confirmed. Usage patterns are relatively similar.

### UFML 5 Comparison interactive

```{r utest-e, echo=FALSE, results='hide'}

wilcox.test(Fysiologischeopwinding ~ Q24, data = data_filtered)
```

```{r interactive-violin-e}

e <- ggplot(data_filtered, aes(x = factor(Q24), y = Fysiologischeopwinding, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 5) + 
  labs(title = "UFML 5 Fysiological Arousal", 
       x = "", 
       y = "Frequency of use (1 = Never, 5 = Very often)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 5), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(e)
```
***
**Expectation**  
-	Students also use music more frequently for its functions in physiological arousal. (more motivation from music and more intense activities)  

**Interpretation**  
- Students and employed individuals show similar use of music for fysiological arousal.  
- Students have slightly more density around the top end (4–5), but also a small cluster at the low end.  
- Employed individuals have a slightly narrower distribution but similar central tendency.  
- The p-value = 0.27, indicating no statistically significant difference.  

Both groups use music similarly for physiological arousal. The data shows no meaningful difference in usage patterns.


### SPWB 1 Comparison interactive

```{r utest-f, echo=FALSE, results='hide'}

wilcox.test(Autonomie ~ Q24, data = data_filtered)
```

```{r interactive-violin-f}

f <- ggplot(data_filtered, aes(x = factor(Q24), y = Autonomie, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 6) + 
  labs(title = "SPWB 1 Autonomy", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(f)
```
***
**Expectation**  
Employed individuals likely feel more autonomoy (more independence and daily control).  

**Interpretation**  
- Students and employed individuals report similar levels of autonomy.  
- Both groups cluster around values 4 to 5, with nearly identical medians.  
- Slightly more spread is visible in the student group, but central tendencies are close.  
- The Wilcoxon p-value = 0.51, indicating no statistically significant difference.  

There is no meaningful difference in perceived autonomy between students and employed individuals. Agreement levels are consistently high across both groups.  

### SPWB 2 Comparison interactive

```{r utest-g, echo=FALSE, results='hide'}

wilcox.test(Omgevingsbeheersing ~ Q24, data = data_filtered)
```

```{r interactive-violin-g}

g <- ggplot(data_filtered, aes(x = factor(Q24), y = Omgevingsbeheersing, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 6) + 
  labs(title = "SPWB 2 Environmental management", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(g)
```
***
**Expectation**  
Employed individuals are expected to score higher (more structure and control in daily environment).  

**Interpretation**  
- Employed individuals report higher levels of environmental management than students.  
- Employed individuals have a higher median and more responses clustered at the top (5–6).  
- Students show a wider spread with more responses around 3–4.  
- The p-value = 0.0074, indicating a statistically significant difference.  

Employed individuals feel more capable of managing their surroundings, suggesting greater control over life situations.  


### SPWB 3 Comparison interactive

```{r utest-i, echo=FALSE, results='hide'}

wilcox.test(`Persoonlijke groei` ~ Q24, data = data_filtered)
```

```{r interactive-violin-i}

i <- ggplot(data_filtered, aes(x = factor(Q24), y = `Persoonlijke groei`, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 6) + 
  labs(title = "SPWB 3 Personal Growth", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(i)
```
***
**Expectation**  
Students may score slightly higher (in an active phase of learning and self-development).  

**Interpretation**  
- Students and employed individuals report similar levels of personal growth.  
- Both groups cluster around 4 to 5, with very similar medians and means.  
- The distributions show comparable spread and central tendency.  
- The p-value = 0.49, indicating no statistically significant difference.  

There is no meaningful difference in perceived personal growth between students and employed individuals. Both groups report fairly high levels.  

### SPWB 4 Comparison interactive

```{r utest-h, echo=FALSE, results='hide'}

wilcox.test(`Positieve relaties` ~ Q24, data = data_filtered)
```

```{r interactive-violin-h}



h <- ggplot(data_filtered, aes(x = factor(Q24), y = `Positieve relaties`, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 6) + 
  labs(title = "SPWB 4 Positive relations", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(h)
```
***
**Expectation**  
Students may score slightly higher (more social opportunities and peer interaction).  

**Interpretation**  
- Students and employed individuals report similar levels of positive relations.  
- Both groups cluster around 4 to 6, with similar medians and means.  
- Students show slightly more responses at the top end (5–6).  
- The p-value = 0.23, indicating no statistically significant difference.  

Both groups report high levels of positive relationships, with no meaningful difference in perceived social connection.  


### SPWB 5 Comparison interactive

```{r utest-j, echo=FALSE, results='hide'}

wilcox.test(`Doel in het leven` ~ Q24, data = data_filtered)
```

```{r interactive-violin-j}

j <- ggplot(data_filtered, aes(x = factor(Q24), y = `Doel in het leven`, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 6) + 
  labs(title = "SPWB 5 Goal in Life", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(j)
```
***
**Expectation** 
Students may score slightly higher (actively shaping future plans and ambitions).  

**Interpretation**  
- Students and employed individuals report similar levels of having a goal in life.  
- Both groups cluster around 4 to 5, with students showing slightly more responses near the top.  
- Medians and means are close, with modest variation in spread.  
- The p-value = 0.12, indicating no statistically significant difference.  

There is no significant difference in sense of life goals between students and employed individuals, though students may report slightly higher levels.  



### SPWB 6 Comparison interactive

```{r utest-k, echo=FALSE, results='hide'}

wilcox.test(Zelfacceptatie ~ Q24, data = data_filtered)
```

```{r interactive-violin-k}

k <- ggplot(data_filtered, aes(x = factor(Q24), y = `Zelfacceptatie`, fill = factor(Q24))) + 
  geom_violin(trim = TRUE, color = "black", alpha = 0.7) + 
  theme_minimal() +
  stat_compare_means(method = "wilcox.test", label.y = 6) + 
  labs(title = "SPWB 6 Self Acceptance", 
       x = "", 
       y = "Level of agreement (1 = Strongly disagree, 6 = Strongly agree)", 
       fill = "Group") + 
  scale_x_discrete(labels = c("1" = "Student", "2" = "Employed")) + 
  scale_fill_manual(values = c("1" = "skyblue", "2" = "orange")) + 
  theme(legend.position = "none") + 
  geom_boxplot(width = 0.1, color = "black", outlier.shape = NA, position = position_dodge (width = 0.9)) + 
  scale_y_continuous(limits = c(1, 6), expand = expansion(mult = c(0, 0.05))) + 
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "red")

ggplotly(k)
```
***
**Expectation**  
Employed individuals may score higher (more life experience and self-confidence).  

**Interpretation**  
- Employed individuals report higher self-acceptance than students.  
- Employed individuals have a higher median and more responses clustered at the top (4–6).  
- Students show a wider spread with more responses in the lower range (2–4).  
- The p-value = 0.03, indicating a statistically significant difference.  

Employed individuals feel more accepting of themselves, possibly reflecting greater life experience and stability.  

### P-values

```{r p-values, include="false"}

ufml_vars <- c("Identiteit_socialeverbinding", "Emotieregulatie", "Focus_concentratie",
               "Achtergrond_gezelschap", "Fysiologischeopwinding")

spwb_vars <- c("Autonomie", "Omgevingsbeheersing", "Persoonlijke groei",
               "Positieve relaties", "Doel in het leven", "Zelfacceptatie")

alle_vars <- c(ufml_vars, spwb_vars)

data_filtered$Q24 <- factor(data_filtered$Q24, levels = c("1", "2"), labels = c("Student", "Employed"))

results <- lapply(alle_vars, function(var) {
  group1 <- data_filtered %>% filter(Q24 == "Student") %>% pull(var)
  group2 <- data_filtered %>% filter(Q24 == "Employed") %>% pull(var)
  
  test <- wilcox.test(group1, group2)
  p <- test$p.value
  
  sig <- case_when(
    p < 0.001 ~ "***",
    p < 0.01  ~ "**",
    p < 0.05  ~ "*",
    TRUE      ~ ""
  )
  
  data.frame(Subscale = var,
           P_value = paste0(round(p, 4), sig))

})

p_table <- do.call(rbind, results)

print(p_table)

```

```{r p-values-table}
p_table %>%
  kable("html", caption = "Mann-Whitney U-test p-values per subscale") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```
```{r save_p_table_png, echo=FALSE, message=FALSE, warning=FALSE}
library(gridExtra)
library(grid)

png("p_table_output.png", width = 300, height = 400)
grid.table(p_table)
dev.off()
```


***
**P-values in violin plots**  
Of the five UFML subscales, two show a significant difference between students and workers: Identity/Social Connection (p = 0.041) and Focus/Concentration (p = 0.023). Within the SPWB scales, Environmental Control (p = 0.0074) and Self-acceptance (p = 0.03) were found to be significantly different between the groups. No statistically significant difference was found for the remaining scales. 

### Spearman's rho and z-values

```{r r-z-values,include="false"}

data_clean$Q24 <- factor(as.numeric(data_clean$Q24),
                         levels = c(1, 2),
                         labels = c("Student", "Employed"))

data_work <- data_clean %>% 
  filter(!is.na(Q24))

ufml_vars <- c("Identiteit_socialeverbinding", "Emotieregulatie", "Focus_concentratie",
               "Achtergrond_gezelschap", "Fysiologischeopwinding")

spwb_vars <- c("Autonomie", "Omgevingsbeheersing", "Persoonlijke groei",
               "Positieve relaties", "Doel in het leven", "Zelfacceptatie")

data_work[c(ufml_vars, spwb_vars)] <- lapply(data_work[c(ufml_vars, spwb_vars)], as.numeric)

fisher_z_test <- function(r1, n1, r2, n2) {
  z1 <- atanh(r1)
  z2 <- atanh(r2)
  se <- sqrt(1 / (n1 - 3) + 1 / (n2 - 3))
  z <- (z1 - z2) / se
  p <- 2 * (1 - pnorm(abs(z)))
  return(c(z = z, p = p))
}

results <- list()

for (ufml in ufml_vars) {
  for (spwb in spwb_vars) {
    
    student <- data_work %>% filter(Q24 == "Student") %>%
      select(all_of(c(ufml, spwb))) %>%
      filter(complete.cases(.))
    
    employed <- data_work %>% filter(Q24 == "Employed") %>%
      select(all_of(c(ufml, spwb))) %>%
      filter(complete.cases(.))
    
    if (nrow(student) >= 4 & nrow(employed) >= 4 &&
        sd(student[[ufml]]) > 0 & sd(student[[spwb]]) > 0 &&
        sd(employed[[ufml]]) > 0 & sd(employed[[spwb]]) > 0) {
      
      cor_student <- cor.test(student[[ufml]], student[[spwb]], method = "spearman")
      cor_employed <- cor.test(employed[[ufml]], employed[[spwb]], method = "spearman")
      r1 <- as.numeric(cor_student$estimate)
      r2 <- as.numeric(cor_employed$estimate)
      fisher <- fisher_z_test(r1, nrow(student), r2, nrow(employed))
      
      results[[paste(ufml, spwb, sep = "_")]] <- data.frame(
        UFML = ufml,
        SPWB = spwb,
        rho_student = round(cor_student$estimate, 3),
        p_student = round(cor_student$p.value, 4),
        rho_employed = round(cor_employed$estimate, 3),
        p_employed = round(cor_employed$p.value, 4),
        z_score = round(fisher["z"], 3),
        p_difference = round(fisher["p"], 4)
      )
    } else {
      results[[paste(ufml, spwb, sep = "_")]] <- data.frame(
        UFML = ufml,
        SPWB = spwb,
        rho_student = NA,
        p_student = NA,
        rho_employed = NA,
        p_employed = NA,
        z_score = NA,
        p_difference = NA
      )
    }
  }
}

correlatie_tabel <- bind_rows(results)

correlatie_tabel <- correlatie_tabel %>%
  mutate(
    sig_student = case_when(
      p_student < 0.001 ~ "***",
      p_student < 0.01 ~ "**",
      p_student < 0.05 ~ "*",
      TRUE ~ ""
    ),
    sig_employed = case_when(
      p_employed < 0.001 ~ "***",
      p_employed < 0.01 ~ "**",
      p_employed < 0.05 ~ "*",
      TRUE ~ ""
    ),
    rho_student_label = ifelse(!is.na(rho_student),
                               paste0("ρ = ", round(rho_student, 2), sig_student), NA),
    rho_employed_label = ifelse(!is.na(rho_employed),
                                paste0("ρ = ", round(rho_employed, 2), sig_employed), NA)
  )


print(correlatie_tabel)

```

```{r correlatie_tabel_output, results='asis'}
correlatie_tabel %>%
  select(UFML, SPWB,
         `Student` = rho_student_label,
         `Employed` = rho_employed_label,
         `Fisher z` = z_score,
         `p (difference)` = p_difference) %>%
  kable("html", caption = "Correlations per group with Fisher’s z-test (Spearman’s ρ)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

```{r save_correlatie_png, echo=FALSE, message=FALSE, warning=FALSE}
library(gridExtra)
library(grid)

correlatie_tabel_view <- correlatie_tabel %>%
  select(UFML, SPWB,
         `Student` = rho_student_label,
         `Employed` = rho_employed_label,
         `Fisher z` = z_score,
         `p (difference)` = p_difference)

png("correlatie_tabel.png", width = 700, height = 800)
grid.table(correlatie_tabel_view)
dev.off()
```



***
**Within-group correlations**  
Among students, several UFML subscales showed moderate to strong correlations with SPWB subscales. Notably:  

Identity/Social Connection correlated with Positive Relationships.  
Emotion Regulation correlated with Self-Acceptance.  
Focus/Concentration correlated with Purpose in Life.  

Correlations in the employed group followed similar patterns but were generally weaker, with fewer statistically significant associations.  

**Between-group differences (Fisher z-tests)**  
Most differences in correlation strength between students and employed participants were not statistically significant.  

In a few cases, stronger correlations were observed in the student group, particularly between Emotion Regulation and Self-Acceptance.  

**Interpretation**  
- UFML subscales are positively associated with psychological well-being (SPWB) across both groups.  
- The relationships are more pronounced in students, suggesting greater psychological reliance on social media functions.  
- Despite variations in strength, the overall pattern of associations appears consistent across groups.  

### UFML 1 vs SPWB 1 Comparison interactive


```{r interactive-correlation-l}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

l <- ggplot(data_filtered, aes(x = Autonomie, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Autonomy and Identity/Social connection per group",
    x = "Autonomy\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(l)

```
***
**Expectation**


**Interpretation**


### UFML 1 vs SPWB 2 Comparison interactive


```{r interactive-correlation-m}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

m <- ggplot(data_filtered, aes(x = Omgevingsbeheersing, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Environmental Management and Identity/Social connection per group",
    x = "Environmental Management\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(m)

```
***
**Expectation**


**Interpretation**


### UFML 1 vs SPWB 3 Comparison interactive


```{r interactive-correlation-n}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

n <- ggplot(data_filtered, aes(x = `Persoonlijke groei`, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Personal Growth and Identity/Social connection per group",
    x = "Personal Growth\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(n)

```
***
**Expectation**


**Interpretation**


### UFML 1 vs SPWB 4 Comparison interactive


```{r interactive-correlation-o}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

o <- ggplot(data_filtered, aes(x = `Positieve relaties`, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Positive Relations and Identity/Social connection per group",
    x = "Positive Relations\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(o)

```
***
**Expectation**


**Interpretation**


### UFML 1 vs SPWB 5 Comparison interactive


```{r interactive-correlation-p}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

p <- ggplot(data_filtered, aes(x = `Doel in het leven`, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Goal in Life and Identity/Social connection per group",
    x = "Goal in Life\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(p)

```
***
**Expectation**


**Interpretation**


### UFML 1 vs SPWB 6 Comparison interactive


```{r interactive-correlation-q}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

q <- ggplot(data_filtered, aes(x = Zelfacceptatie, y = Identiteit_socialeverbinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Self Acceptance and Identity/Social connection per group",
    x = "Self Acceptance\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Identity and Social connection\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(q)

```
***
**Expectation**


**Interpretation**



### UFML 2 vs SPWB 1 Comparison interactive


```{r interactive-correlation-r}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

r <- ggplot(data_filtered, aes(x = Autonomie, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Autonomy and Emotion Regulation per group",
    x = "Autonomy\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(r)

```
***
**Expectation**


**Interpretation**


### UFML 2 vs SPWB 2 Comparison interactive


```{r interactive-correlation-s}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

s <- ggplot(data_filtered, aes(x = Omgevingsbeheersing, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Environmental Management and Emotion Regulation per group",
    x = "Environmental Management\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(s)

```
***
**Expectation**


**Interpretation**


### UFML 2 vs SPWB 3 Comparison interactive


```{r interactive-correlation-t}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

t <- ggplot(data_filtered, aes(x = `Persoonlijke groei`, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Personal Growth and Emotion Regulation per group",
    x = "Personal Growth\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(t)

```
***
**Expectation**


**Interpretation**


### UFML 2 vs SPWB 4 Comparison interactive


```{r interactive-correlation-u}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

u <- ggplot(data_filtered, aes(x = `Positieve relaties`, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Positive Relations and Emotion Regulation per group",
    x = "Positive Relations\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(u)

```
***
**Expectation**


**Interpretation**


### UFML 2 vs SPWB 5 Comparison interactive


```{r interactive-correlation-v}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

v <- ggplot(data_filtered, aes(x = `Doel in het leven`, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Goal in Life and Emotion Regulation per group",
    x = "Goal in Life\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(v)

```
***
**Expectation**


**Interpretation**


### UFML 2 vs SPWB 6 Comparison interactive


```{r interactive-correlation-w}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

w <- ggplot(data_filtered, aes(x = Zelfacceptatie, y = Emotieregulatie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Self Acceptance and Emotion Regulation per group",
    x = "Self Acceptance\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Emotion Regulation\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(w)

```
***
**Expectation**


**Interpretation**


### UFML 3 vs SPWB 1 Comparison interactive


```{r interactive-correlation-x}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

x <- ggplot(data_filtered, aes(x = Autonomie, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Autonomy and Focus/Concentration per group",
    x = "Autonomy\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus/Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(x)

```
***
**Expectation**


**Interpretation**


### UFML 3 vs SPWB 2 Comparison interactive


```{r interactive-correlation-y}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

y <- ggplot(data_filtered, aes(x = Omgevingsbeheersing, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Environmental Management and Focus/Concentration per group",
    x = "Environmental Management\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus and Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(y)

```
***
**Expectation**


**Interpretation**


### UFML 3 vs SPWB 3 Comparison interactive


```{r interactive-correlation-z}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

z <- ggplot(data_filtered, aes(x = `Persoonlijke groei`, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Personal Growth and Focus/Concentration per group",
    x = "Personal Growth\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus and Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(z)

```
***
**Expectation**


**Interpretation**


### UFML 3 vs SPWB 4 Comparison interactive


```{r interactive-correlation-aa}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

aa <- ggplot(data_filtered, aes(x = `Positieve relaties`, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Positive Relations and Focus/Concentration per group",
    x = "Positive Relations\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus and Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(aa)

```
***
**Expectation**


**Interpretation**


### UFML 3 vs SPWB 5 Comparison interactive


```{r interactive-correlation-ab}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ab <- ggplot(data_filtered, aes(x = `Doel in het leven`, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Goal in Life and Focus/Concentration per group",
    x = "Goal in Life\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus and Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ab)

```
***
**Expectation**


**Interpretation**


### UFML 3 vs SPWB 6 Comparison interactive


```{r interactive-correlation-ac}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ac <- ggplot(data_filtered, aes(x = Zelfacceptatie, y = Focus_concentratie, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Self Acceptance and Focus/Concentration per group",
    x = "Self Acceptance\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Focus and Concentration\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ac)

```
***
**Expectation**


**Interpretation**


### UFML 4 vs SPWB 1 Comparison interactive


```{r interactive-correlation-ad}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ad <- ggplot(data_filtered, aes(x = Autonomie, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Autonomy and Background/Company per group",
    x = "Autonomy\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Achtergrond and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ad)

```
***
**Expectation**


**Interpretation**


### UFML 4 vs SPWB 2 Comparison interactive


```{r interactive-correlation-ae}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ae <- ggplot(data_filtered, aes(x = Omgevingsbeheersing, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Environmental Management and Background/Company per group",
    x = "Environmental Management\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Bachground and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ae)

```
***
**Expectation**


**Interpretation**


### UFML 4 vs SPWB 3 Comparison interactive


```{r interactive-correlation-af}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

af <- ggplot(data_filtered, aes(x = `Persoonlijke groei`, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Personal Growth and Background/Company per group",
    x = "Personal Growth\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Background and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(af)

```
***
**Expectation**


**Interpretation**


### UFML 4 vs SPWB 4 Comparison interactive


```{r interactive-correlation-ag}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ag <- ggplot(data_filtered, aes(x = `Positieve relaties`, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Positive Relations and Background/Company per group",
    x = "Positive Relations\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Background and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ag)

```
***
**Expectation**


**Interpretation**


### UFML 4 vs SPWB 5 Comparison interactive


```{r interactive-correlation-ah}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ah <- ggplot(data_filtered, aes(x = `Doel in het leven`, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Goal in Life and Background/Company per group",
    x = "Goal in Life\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Background and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ah)

```
***
**Expectation**


**Interpretation**


### UFML 4 vs SPWB 6 Comparison interactive


```{r interactive-correlation-ai}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ai <- ggplot(data_filtered, aes(x = Zelfacceptatie, y = Achtergrond_gezelschap, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Self Acceptance and Background/Company per group",
    x = "Self Acceptance\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Background and Company\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ag)

```
***
**Expectation**


**Interpretation**


### UFML 5 vs SPWB 1 Comparison interactive


```{r interactive-correlation-aj}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

aj <- ggplot(data_filtered, aes(x = Autonomie, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Autonomy and Fysiological Arousal per group",
    x = "Autonomy\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(aj)

```
***
**Expectation**


**Interpretation**


### UFML 5 vs SPWB 2 Comparison interactive


```{r interactive-correlation-ak}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ak <- ggplot(data_filtered, aes(x = Omgevingsbeheersing, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Environmental Management and Fysiological Arousal per group",
    x = "Environmental Management\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ak)

```
***
**Expectation**


**Interpretation**


### UFML 5 vs SPWB 3 Comparison interactive


```{r interactive-correlation-al}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

al <- ggplot(data_filtered, aes(x = `Persoonlijke groei`, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Personal Growth and Fysiological Arousal per group",
    x = "Personal Growth\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(al)

```
***
**Expectation**


**Interpretation**


### UFML 5 vs SPWB 4 Comparison interactive


```{r interactive-correlation-am}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

am <- ggplot(data_filtered, aes(x = `Positieve relaties`, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Positive Relations and Fysiological Arousal per group",
    x = "Positive Relations\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(am)

```
***
**Expectation**


**Interpretation**


### UFML 5 vs SPWB 5 Comparison interactive


```{r interactive-correlation-an}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

an <- ggplot(data_filtered, aes(x = `Doel in het leven`, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Goal in Life and Fysiological Arousal per group",
    x = "Goal in Life\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(an)

```
***
**Expectation**


**Interpretation**


### UFML 5 vs SPWB 6 Comparison interactive


```{r interactive-correlation-ao}

data_filtered <- data_clean %>%
  filter(Q24 %in% c(1, 2))

data_filtered$Q24 <- factor(data_filtered$Q24, 
                            levels = c(1, 2), 
                            labels = c("Student", "Employed"))

ao <- ggplot(data_filtered, aes(x = Zelfacceptatie, y = Fysiologischeopwinding, color = Q24)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(
    values = c("Student" = "skyblue", "Employed" = "orange"),
    name = "Group"
  ) +
  scale_x_continuous(breaks = 1:6, limits = c(1, 6)) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  labs(
    title = "Relation between Self Acceptance and Fysiological Arousal per group",
    x = "Self Acceptance\n(1 = Strongly disagree, 6 = Strongly agree)",
    y = "Fysiological Arousal\n(1 = Never, 5 = Very often)"
  ) +
  theme_minimal()

ggplotly(ao)

```
***
**Expectation**


**Interpretation**
